Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Introduce model slightly differently

The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
of his schedule in the array of constrained integer variables $\timeSlot[0]$ to
$\timeSlot[{t-1}]$ (\eqref{var:timeSlot} below), and a state view in the array
of constraint integer variables $\state[0]$ to $\state[{f-1}]$
(\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
flight $i$ and corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
$\timeSlot[{m(i+1)-1}]$.

\begin{figure}
\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
\begin{framed}
\begin{align}
    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
    \end{alignedat} \nonumber \\
&\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
&\validStateSequence(\state) \label{C3} \tag{C3}
\end{align}
\end{framed}
\caption{A skipper-oriented model. A copy of these variables and constraints is
created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
the number of matches in a flight. The number of flights is $f = \lceil
n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}
\end{figure}

>>>>

The first thing we model, in Figure~\ref{model:skipper}, is a skipper. Each
skipper $\sigma$ has a temporal view of his schedule in the array of
constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state
view in the array of constraint integer variables $\state[0]$ to
$\state[{f-1}]$. The state of this skipper in flight $i$ is found in
$\state[i]$, and this corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
$\timeSlot[{m(i+1)-1}]$.

\begin{figure}
\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
\begin{framed}
\begin{align}
    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
    \end{alignedat} \nonumber \\
&\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
&\validStateSequence(\state) \label{C3} \tag{C3}
\end{align}
\end{framed}
\caption{A skipper-oriented model. A copy of these variables and constraints is
created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
the number of matches in a flight. The number of flights is $f = \lceil
n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:skipper}
\end{figure}
